### 2012-03-04 3.1.1.tex
More arranging.
Writing on chapter 3

% 3.1.1: Backness harmony

@@

One of the most salient aspects of Turkish phonology is the presence of vowel harmony. \citeauthor{Lees1966a} (\citeyear[][284]{Lees1966b}, \citeyear[][35]{Lees1966a}) proposes a number of phonological rules to describe the harmony processes that act on roots and regularly spread rightward to suffixes (Turkish has no prefixes); one such rule consists of rightward spreading of the feature [\textsc{Back}].

@@

1. \citet[][289]{Anderson1974} 
2. \citet[][]{Kiparsky1981} makes a similar objection regarding Finnish vowel harmony.
3. \citet{Clements1982}
4. \citet{Inkelas1997}

>>>>

\subsection{Backness harmony}

One of the most salient aspects of spoken Turkish is the presence of vowel harmony. To a first approximation, 
the high vowels of a Turkish prosodic word are all either all round or all unround. Here we will focus on backness harmony

vowels agree

all the vowels in a Turkish prosodic words agree for backness, and in addition, high vowels agree in roundness.

@@

\citeauthor{Lees1966a} (\citeyear[][284]{Lees1966b}, \citeyear[][35]{Lees1966a}) proposes a number of phonological rules to describe the harmony processes that act on roots and regularly spread rightward to suffixes (Turkish has no prefixes); one such rule consists of rightward spreading of the feature [\textsc{Back}].

@@

1. \citet[][289]{Anderson1974} 
%2. \citet[][]{Kiparsky1981} makes a similar objection regarding Finnish vowel harmony.
3. \citet{Clements1982}
4. \citet{Inkelas1997}

### 2012-03-04 3.1.tex
More arranging.
Writing on chapter 3

% 3.1: Wordlikeness predictions

\citet{Zimmer1969}

I assume without discussion the following binary feature specifications for the vowel phonemes of Turkish.

@@

@@

\subsection{Backness harmony}  \input{3.1.1}
\subsection{Labial attraction} \input{3.1.2}

>>>>

\section{Turkish vowel sequence structure constraints}

Below, I detail two sequence structure constraints on root vowels in Turkish proposed by \citet{Lees1966a,Lees1966b}, relating these generalizations to Turkish alternation phonology and various sources of external evidence. A standard binary feature specification for the Turkish vowel system, given below, is assumed throughout.

@@

\input{3.1.1}
\input{3.1.2}

@@

### 2012-03-04 3.2.2.tex
More arranging.
Writing on chapter 3

% 3.2.2: Wordlikeness results

@@

\subsubsection{Roundness harmony}

@@

Roundness harmony wordlikeness forced choices \citep[314]{Zimmer1969}: \vspace{6pt} \\ 
\begin{tabular}{l r l r}
\toprule
\multicolumn{2}{l}{harmonic} & \multicolumn{2}{l}{disharmonic} \\
\midrule
pemez & 30                   & pemaz & 2 \\
teriz & 28                   & terız & 3 \\
tokaz & 26                   & tokez & 6 \\
tipez & 24                   & tipaz & 8 \\
terüz & 19                   & teruz & 13 \\
\bottomrule
\end{tabular}

>>>>

\subsection{Wordlikeness results}

@@

\subsubsection{Backness harmony}

@@

Backness harmony wordlikeness forced choices \citep[314]{Zimmer1969}: \vspace{6pt} \\ 
\begin{tabular}{l r l r}
\toprule
\multicolumn{2}{l}{harmonic} & \multicolumn{2}{l}{disharmonic} \\
\midrule
pemez & 30                   & pemaz & 2  \\
teriz & 28                   & terız & 3  \\
tokaz & 26                   & tokez & 6  \\
tipez & 24                   & tipaz & 8  \\ 
terüz & 19                   & teruz & 13 \\ % roundness violator
\bottomrule
\end{tabular}

### 2012-03-04 3.tex
More arranging.
Writing on chapter 3

One of the original motivations for the development of a theory of static co-occurrence restrictions as developed by \citet{SPR}, \citet{Stanley1967} and others is to account for speakers' abilities to distinguish between accidental and structural gaps. \citet{Chomsky1965} propose that a theory of phonology must account for speakers' abilities to distinguish between accidental and structural gaps in their language, citing a contrast between \emph{blick}, which is judged to be a possible but unattested word of English, and \emph{bnick}, which is judged to be impossible. \emph{SPE} (p.~3810f.) places this contrast in a system of a system of sequence structure rules that also are used to eliminate lexical redundancy. In the phonological theory of the era, there is no process that could generate the \emph{blick} $\sim$ \emph{bnick} contrast or numerous other lexical regularities \citep[][283f.]{Anderson1974}.\footnote{This sequence of arguments has already been critiqued in Chapter \ref{1}, where it was shown that prosodic licensing and Stampean occultation places this contrast in core phonology, and that the principles by which speakers recognize impossible words must be stated on surface representations, not underlying representations. Further, \citet[][528f.]{Halle1975} rejects his own principle that lexical entries should be free of all redundancies (see \citealt[][201]{Reiss2003a} and \citealt{Vaux2003} for further discussion). This rejected principle of a redundancy-free lexicon is one of the two principles that motivates Morpheme Structure Constraints; the other is the subject of this and the following chapter.}

@@

\section{Turkish vowel MSCs} \input{3.1}
\section{Evaluation}         \input{3.2}
\section{Conclusion}         \input{3.3}

>>>>

This is not a universal, but rather something English speakers must learn: some languages, such as Moroccan Arabic, do in fact permit \emph{bn} onsets (e.g., \emph{bni} 'building', \emph{bnat} 'daughters', \emph{bniqa} 'closet').

%bni 'building'
%bnin 'delicious'
%bniqa 'closet' 
%bnat 'girl' 
%bnita 'girl (dim.)'

a matter of universal

In their illustration of

One of the

One of the most compelling findings

The contrast between \emph{blick} and \emph{bnick} is what has been called a "projection problem" \citep{Baker1979}

This is what we might call a projec
In presenting the components of a 
a term which

by subphonemic details

\citet{Davidson2005,Davidson2006a} shows that excresent schwa is acoustically and articulatorily distinct from "lexical schwa":
\citet{Wilson2011} show taht speakers use this

%English speakers' z^@k is more similar to \emph{scum} than \emph{succumb}

/sC-/ onsets than /s@C-/.

% Davidson 2005: z^@C is more like sC than s@C (ultrasound of articulations)
% Davidson 2006a: lexical and excresant schwa are not the same (acoustics)

% Davidson 2010: production
% Wilson & Davidson 2011:

\citet{Berent2007a}
\citet{Berent2007b}
\citet{Berent2008a}

% Berent et al. 2007
% 598: Highly marked inputs are repaired in perception to abide by the grammatical restrictions of the language
% Exps 1-2: syllable count task (misperception due to linguistic experience; "disyllables were more likely to be perceived as monosyllables if their monosyllabic counterparts had a less marked cluster" in both Russian and English, not what OT predicts)
% Exps 3-4: AB task
% Exps 5-6: priming effect (non-epenthetic and epenethetic things represented the same)
% Berent and Lennertz 2007: (640: If the high rate of monosyllabic errors to unmarked onsets is only due to phonetic failures to encode the input, then it is puzzling why the same onsets also yield the highest rate of accurate response.)
% Berent et al. 2008a:
\citet{Peperkamp2007}
% Peperkamp 2007: during one stage of processing phonology is undone with help from the lexicon...it only takes licit inputs and is irrelevant (p. 633)
\citet{Dupoux1999}
% Dupoux et al. 1999: Japanese speakers still can't distinguish between ebzo and ebuzo in an ABX task using the SAME a or b.

\citet{Daland2011}

does not so much as explain the thing itself but rather suggests the

I believe a number of the predictions of this model are wrong
the original and still-compelling 
findings that drove

 motivations for the development of a theory of static co-occurrence restrictions as developed by \citet{SPR}, \citet{Stanley1967} and others is to account for speakers' abilities to distinguish between accidental and structural gaps. \citet{Chomsky1965} propose that a theory of phonology must account for speakers' abilities to distinguish between accidental and structural gaps in their language, citing a contrast between \emph{blick}, which is judged to be a possible but unattested word of English, and \emph{bnick}, which is judged to be impossible. \emph{SPE} (p.~3810f.) places this contrast in a system of a system of sequence structure rules that also are used to eliminate lexical redundancy. In the phonological theory of the era, there is no process that could generate the \emph{blick} $\sim$ \emph{bnick} contrast or numerous other lexical regularities \citep[][283f.]{Anderson1974}.

This sequence of arguments has already been critiqued in Chapter \ref{1}, where it was shown that prosodic licensing and Stampean occultation places this contrast in core phonology, and that the principles by which speakers recognize impossible words must be stated on surface representations, not underlying representations. Further, \citet[][528f.]{Halle1975} rejects his own principle that lexical entries should be free of all redundancies (see \citealt[][201]{Reiss2003a} and \citealt{Vaux2003} for further discussion). This rejected principle of a redundancy-free lexicon is one of the two principles that motivates Morpheme Structure Constraints; the other is the subject of this and the following chapter.

@@

\input{3.1}
\input{3.2}
\input{3.3}
